Existing Models

### 2023-11-28 owen/Write Ups/03_existing_models.qmd
rename this file to avoid any confusion
some small changes
rerun some of this analysis, with the simpler model here

---
title: "Model Checking"
author: Owen G. Ward
date: 05/26/2023
format: 
  # html:
  #   toc: true
  #   toc-location: left
  pdf
bibliography: refs.bib
---

@@

fit3_ave$save_object("../model_fits/init_model_n10.RDS")
```

@@

@@

mcmc_hist(fit3_ave$draws(c("alpha", "mu2", "tau2")))
mcmc_hist(fit3_ave$draws(c("beta", "mu1", "tau1", "gamma1", "gamma2")))
```

@@

fit4$save_object(file = "../model_fits/model4.RDS")
```

@@

fit4 <- readRDS("../model_fits/model4.RDS")

mcmc_hist(fit4$draws(c("delta", "mu3", "tau3"))) +
  labs(title = "Effect of Previous Game")

mcmc_hist(fit4$draws(c("beta", "mu1", "tau1"))) +
  labs(title = "Effect of Previous n games, excluding most recent game")

>>>>

---
title: "Existing Models"
author: Owen G. Ward
date: 05/26/2023
format: 
  # html:
  #   toc: true
  #   toc-location: left
  pdf
bibliography: refs.bib
---

@@

# fit3_ave$save_object("../model_fits/init_model_n10.RDS")
```

@@

# fit3_ave <- readRDS("../model_fits/init_model_n10.RDS")

@@

mcmc_hist(fit3_ave$draws(c("alpha", "mu2")))
mcmc_hist(fit3_ave$draws(c("beta", "mu1", "gamma1", "gamma2")))
```

@@

# fit4$save_object(file = "../model_fits/model4.RDS")
```

@@

# fit4 <- readRDS("../model_fits/model4.RDS")

mcmc_hist(fit4$draws(c("delta", "mu3"))) +
  labs(title = "Effect of Previous Game")

mcmc_hist(fit4$draws(c("beta", "mu1"))) +
  labs(title = "Effect of Previous n games, excluding most recent game")
